\documentclass[a4paper,11pt]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}
\usepackage{hyperref}

\title{On word disambiguation features}
\author{Maria Boritchev}

\begin{document}

\maketitle
%\tableofcontents

%\begin{abstract}
%\end{abstract}

\section{Integrating Multiple Knowledge Sources to
Disambiguate Word Sense: An Exemplar-Based Approach}
\url{http://arxiv.org/pdf/cmp-lg/9606032.pdf} \\
Authors: \textsc{Hwee Tou Ng}, \textsc{Hian Beng Lee}. \\

\noindent \textbf{Problem:} Word Sense Disambiguation (WSD).\\
\textbf{Input:} set of unrestricted, real-world English sentences. WARNING: the disambiguation is therefore internal to each sentence. Those sentences are pre-tagged with parts-of-speach (POS) tags ($N$, $V$, $Adj$, $Adv$), using existing software. Also: a list of ambiguous words mapped to their different meanings, those meanings being referenced to with numbers.\\
\textbf{Output:} each ambiguous word $w$ tagged with its correct sense number $i$ (context-dependent).\\

\subsection{Feature extraction: $L_3,L_2,L_1,R_1,R_2,R_3,M,K_1,\dots,K_m,C_1,\dots,C_9,V$}
$L_i$: POS of the word $i$-th position to the left of $w$ in the sentence $s$. \\
$R_i$: POS of the word $i$-th position to the right of $w$ in $s$.\\
$M$: morphological form of $w$ in $s$ (if $w$ is a noun ($N$), then sing./plur.; if $w$ is a verb ($V$), then prst. $3^d$ pers. sing./past participle/etc).\\

\noindent $K_1,\dots,K_m$: features corresponding to a set of keywords that frequently co-occur with $w$ in the same sentence. This set is determined by conditional porbabilities (see below). For a sentence $s$, the value of feature $K_i$ is $1$ if $K_i$ appears in $s$, $0$ otherwise.\\
$V$: verb-object syntactic relation (useful in disambiguation of nouns).

\section{Some observations}
Other features we might take into consideration: types of prepositions in the sentence (place, time, ...).



 


\end{document}
